\section{Limitations}
\label{sec:limitations}

\paragraph{Language and cultural scope.} OenoBench is currently
English-only. The Tier-2 source mix (Wikipedia 34\%, Wikidata 31\%) is
itself English-skewed, and the corpus inherits a geographic bias toward
European (especially French, Italian, Spanish) and New-World canonical
regions. Emerging wine cultures (China, India, much of Eastern Europe)
are under-represented in absolute counts. Multilingual extension is
the largest single gap and is the most natural next-version target.

\paragraph{Source skew within domains.} Producer and wine-business
domains are smaller (515 and 250 questions respectively) than wine
regions (1{,}108) and grape varieties (766) because authoritative
producer-level and business-level open data is scarcer than
appellation-level data. The C4 difficulty re-label
(Section~\ref{sec:audit}) shifted the corpus toward harder items but
cannot create coverage that did not exist; the per-domain accuracy
ceiling on \emph{wine\_business} (\textbf{56.5\% mean across 16 configs},
vs.\ 79\% on producers) reflects both the hardness of the domain and
its sparser fact pool.

\paragraph{Snapshot vs.\ moving target.} Wine regulation,
classifications, and producer ownership change on a multi-year cadence
(INAO appellation revisions, DOCG promotions, estate sales). The
released corpus is a snapshot dated 2026-04-01 and will require
periodic re-extraction; we release the scrapers and provenance
metadata so this is mechanically reproducible.

\paragraph{Closed-book audit calibration.} The B2 ClosedBookSolvability
agent shows $\kappa\approx0.007$ with humans on the gold sheet
(Section~\ref{sec:gold}). Rather than drop the affected questions, we
keep them with explicit disclosure and report the closed-book vs.\
contextual contrast in Section~\ref{sec:eval-cb}. Downstream users who
prefer a strictly source-grounded subset can use the contextual slice;
those who want pure recall can use the closed-book slice. The
documentation is a load-bearing part of the dataset, not a footnote.

\paragraph{Self-preference is not fully neutralised.} The Anthropic
$+9$~pp positive SPS (Section~\ref{sec:eval-sps}) implies the
multi-model generation strategy did not fully neutralise stylistic
fingerprints. We disclose per-config SPS as a first-class diagnostic
rather than removing the affected items, but downstream comparisons
between Anthropic and other-family models on the full corpus should
be treated with the SPS in mind.

\section{Ethics and Responsible Use}
\label{sec:ethics}

\paragraph{Alcohol context.} Wine is an alcoholic beverage. OenoBench
is a knowledge-evaluation tool, not a consumer-facing product. Models
that score highly on OenoBench should not be deployed as
drinking-recommendation systems without separate alignment work
covering health information, age-gating, and jurisdiction-specific
advertising rules.

\paragraph{Source licensing.} Tier-1 government sources are public
records. Tier-2 Wikipedia and Wikidata content is used under
CC-BY-SA / CC0; OenoBench question texts are derivative works produced
by paraphrasing facts, not copies of source paragraphs, and are
released under \textbf{CC-BY-SA-4.0}. Per-fact source URLs are released
alongside the corpus so downstream users can verify and re-attribute.

\paragraph{Personal data.} The corpus contains entity names of
producers, winemakers, and historical figures who are public-record
principals of wine estates. No private individuals are identified. The
gold-sheet reviewer is identified only by professional credential.

\paragraph{Misuse considerations.} A wine-knowledge benchmark is low
risk for direct misuse. The closest plausible misuse is using
high-OenoBench-score models to automate fraudulent product descriptions
or counterfeit provenance claims. We note this for completeness but do
not see a benchmark-side mitigation distinct from general
LLM-deployment safeguards. The construction code's principal misuse
risk is its application to retargeting toward high-stakes domains
(medical, legal) without commensurate human-expert review of the
retargeted source taxonomy; we discuss this scoping concern in
Section~\ref{sec:future}.

\paragraph{LLM use during construction.} Large language models were
used as components of the pipeline (question generation, audit
agents). They were \emph{not} used as sources of factual claims; every
factual assertion in the corpus traces to a non-LLM source URL with a
tier-of-authority label. This separation is enforced by the A3
FactEcho agent (no verbatim source copying) and the closed-book
pre-screen.
