\section{Related Work}
\label{sec:related}

\paragraph{Broad knowledge benchmarks.} MMLU
\citep{hendrycks2021mmlu}, BIG-Bench \citep{srivastava2023bigbench},
AGIEval \citep{zhong2024agieval}, GPQA \citep{rein2024gpqa}, HELM
\citep{liang2023helm}, and Humanity's Last Exam \citep{phan2025hle}
measure factual breadth and reasoning across many subjects. We instead
maximise depth within a single externally-validated knowledge domain
and treat \emph{construction-time bias control} as a first-class
contribution rather than a downstream decontamination step.

\paragraph{Domain-specific benchmarks.} MedQA
\citep{jin2021medqa}, PubMedQA \citep{jin2019pubmedqa}, LegalBench
\citep{guha2023legalbench}, and FinanceBench
\citep{islam2023financebench} ground evaluation in regulated
professions with clear sources of truth. We adopt their
expert-syllabus / source-traceable backbone and add multi-model
generation, multi-agent audit, and self-preference reporting.
OenoBench is, to our knowledge, the first such benchmark for wine.

\paragraph{LLM-as-judge bias and self-preference.} A growing literature
documents that models tend to favour outputs stylistically similar to
their own \citep{panickssery2024selfpref, zheng2023judging,
sharma2024sycophancy}, biasing benchmarks where the same model
generates and grades. We mitigate by distributing generation across
five generator families plus deterministic templates and by reporting
per-model self-vs-other accuracy gaps as a first-class diagnostic
(Section~\ref{sec:eval-sps}).

\paragraph{Benchmark contamination and solvability.} Pre-training
exposure inflates apparent capability \citep{sainz2023contamination,
magar2022contamination, dodge2021documenting}. We mitigate by
generating from atomic facts (a fact-echo agent flags any question
whose longest common substring with the source exceeds 65\%) and by
running an explicit \emph{closed-book solvability} pre-screen and
audit (Section~\ref{sec:eval-cb}). The same audit, calibrated against
a human gold sheet, reveals that LLM judges over-report leakage by an
order of magnitude --- a finding with broader implications for the
LLM-as-judge paradigm.

\paragraph{Wine in NLP.} Wine has previously appeared in NLP via
review-text recommendation \citep{chen2014winerec}, taxonomy learning
\citep{lefever2017winenlp}, and judge-reliability studies
\citep{hodgson2017winereviews}. OenoBench is the first benchmark
targeting \emph{structured factual knowledge} of viticulture,
winemaking, and wine regions evaluated against frontier LLMs.
