\section{Introduction}
\label{sec:intro}

Large language models are increasingly evaluated on knowledge-intensive benchmarks, but the most widely-used resources --- MMLU \citep{hendrycks2021mmlu}, GPQA \citep{rein2024gpqa}, and their successors --- share three properties that limit their usefulness as the field matures: (i) they aggregate breadth at the expense of \emph{depth} within any single discipline, (ii) they are typically authored or curated by a small team using a single generation pipeline, exposing them to systematic blind-spots and stylistic regularities that frontier models can learn to exploit, and (iii) the questions are increasingly suspected of contamination through web-scale pre-training corpora. Recent work on benchmark contamination \citep{TODOcontamination} and on self-preference bias in LLM-as-judge pipelines \citep{TODOselfpref} suggests that as models grow more capable, the marginal value of a benchmark depends increasingly on \emph{how} it was constructed, not only on what it contains.

We argue that domain-specialised benchmarks built around bodies of knowledge that are \emph{externally validated by humans} --- through certification, regulation, or peer-reviewed practice --- offer a useful complement to broad knowledge benchmarks. Examples already exist in medicine \citep{TODOmedqa}, law \citep{TODOlegalbench}, and finance \citep{TODOfinancebench}. We extend this line of work to a domain that has so far received little attention from the benchmarking community, despite being unusually well-defined: \textbf{wine}.

\paragraph{Why wine.} Wine is a multi-disciplinary subject that integrates plant biology, geology and climate science, organic chemistry, food microbiology, sensory neuroscience, regulatory law, and business economics. It is one of very few domains for which (a) authoritative governmental and inter-governmental sources publish structured taxonomic data (e.g.\ INAO, OIV, TTB, regional consortia), (b) university research groups (notably UC Davis, Geisenheim, Bordeaux Sciences Agro) produce open scholarly literature, and (c) professional certification bodies define a graded competence ladder (WSET Levels 1--4, Court of Master Sommeliers, Institute of Masters of Wine) whose published syllabi can be used to ground what ``expert'' should mean. Together these properties make it possible to build a benchmark in which every question is traceable to a verifiable source, while still spanning the recall--reasoning--application spectrum that distinguishes a strong taster, winemaker, or buyer from a memorised glossary.

\paragraph{Contributions.} This paper makes four contributions.
\begin{enumerate}
  \item \textbf{A wine-domain benchmark} of \PH{$\approx$5{,}000} questions covering six pillars (regions, varieties, viticulture, winemaking, producers, business), built from 38{,}104 atomic facts whose provenance is recorded down to the source URL and tier of authority.
  \item \textbf{A multi-strategy, multi-model question-generation pipeline} (Section~\ref{sec:dataset}) that combines five generation strategies and five generator models, with an explicit fact-grounding constraint: the LLM's role is reformatting verified facts, not providing them.
  \item \textbf{A multi-agent quality audit} (Section~\ref{sec:audit}) consisting of nine deterministic, statistical, and tri-judge agents organised into four teams, calibrated against a human gold sheet using Cohen's $\kappa$ and rejecting any agent signal whose human agreement falls below threshold.
  \item \textbf{A bias-aware evaluation protocol} (Section~\ref{sec:eval}) including held-out per-generator splits, an expert-authored 300-question control set, and a \emph{Self-Preference Score} that quantifies the gap between a model's accuracy on its own questions and on questions written by other generators.
\end{enumerate}

OenoBench, the source code for the construction and audit pipelines, the multi-agent audit reports, and the human gold sheet are released under \PH{license + URL pending de-anonymisation}.
