\section{Related Work}
\label{sec:related}

\paragraph{Broad knowledge benchmarks.} MMLU
\citep{hendrycks2021mmlu}, BIG-Bench \citep{srivastava2023bigbench},
AGIEval \citep{zhong2024agieval}, GPQA \citep{rein2024gpqa}, HELM
\citep{liang2023helm}, and Humanity's Last Exam \citep{phan2025hle}
measure factual breadth and reasoning across many subjects. As headline
scores have saturated, attention has shifted toward harder reasoning
benchmarks and toward auditing the construction process. Our work is
complementary: rather than maximising difficulty across many
disciplines, we maximise depth within a single externally-validated
knowledge domain, and treat \emph{construction-time bias control} as a
first-class methodological contribution rather than a downstream
decontamination step.

\paragraph{Domain-specific benchmarks.} MedQA
\citep{jin2021medqa}, PubMedQA \citep{jin2019pubmedqa}, LegalBench
\citep{guha2023legalbench}, and FinanceBench \citep{islam2023financebench}
demonstrate the value of grounding evaluation in a regulated profession
with clear sources of truth. We adopt their organising principle ---
expert syllabus as taxonomy, source-traceable facts as backbone --- and
add multi-model question generation, an automated multi-agent audit, and
self-preference reporting as additional bias controls. To our knowledge,
OenoBench is the first such benchmark for the wine domain.

\paragraph{LLM-as-judge bias and self-preference.} A growing literature
documents that models tend to favour outputs stylistically similar to
their own \citep{panickssery2024selfpref, zheng2023judging,
sharma2024sycophancy}, biasing benchmarks where the same model
generates and grades. We mitigate by distributing generation across
five generator families plus deterministic templates and by reporting
per-model self-vs-other accuracy gaps as a first-class diagnostic
(Section~\ref{sec:eval-sps}).

\paragraph{Benchmark contamination and solvability.} Pre-training
exposure inflates apparent capability \citep{sainz2023contamination,
magar2022contamination, dodge2021documenting}. We mitigate contamination
in two ways: (i) generating questions from atomic facts rather than
copying source text (a fact-echo agent flags any question whose longest
common substring with the source exceeds 65\%), and (ii) running an
explicit \emph{closed-book solvability} pre-screen and audit, allowing
us to report a separate per-config accuracy on world-knowledge-solvable
items (Section~\ref{sec:eval-cb}). We further show that the same audit,
when calibrated against a human gold sheet, reveals that LLM judges
themselves over-report leakage by an order of magnitude --- a finding
with broader implications for the LLM-as-judge paradigm.

\paragraph{Wine in NLP.} Wine has previously appeared in NLP via
review-text recommendation \citep{chen2014winerec}, taxonomy learning
\citep{lefever2017winenlp}, and judge-reliability studies
\citep{hodgson2017winereviews}. OenoBench is the first benchmark
targeting \emph{structured factual knowledge} of viticulture,
winemaking, and wine regions evaluated against frontier LLMs.
