\section{Multi-Agent Quality Audit}
\label{sec:audit}

The audit pipeline runs every generated question through nine automated
agents organised into four teams. Each agent emits a per-question
signal in $\{\textsc{pass}, \textsc{warn}, \textsc{fail}\}$ and signals
are calibrated against a human-reviewed gold sheet using Cohen's
$\kappa$. Agents whose human agreement falls below threshold are
downweighted to advisory-only, on the principle that an automated judge
whose verdict humans cannot reproduce should not gate question
admission. A separate human-review web application
(Appendix~\ref{app:screenshots}) collects the gold-sheet ratings from
WSET-Diploma reviewers and is itself part of the released artifact set.
A team-by-team architecture diagram (Figure~\ref{fig:audit-app},
Appendix~\ref{app:eval}) shows how candidate questions flow through
the four teams to the drop / relabel / keep verdict.

\subsection{Team architecture}
\label{sec:audit-arch}

\begin{table}[h]
  \centering
  \caption{The 14 audit agents across four teams. \textsc{always}:
    run on every question. \textsc{esc}: escalation-gated.}
  \label{tab:agents}
  \footnotesize
  \begin{tabular}{lllp{0.46\linewidth}}
    \toprule
    Team & Agent & Run & Function \\
    \midrule
    \multirow{4}{*}{A. Static}
      & A1 LexicalHygiene        & \textsc{always} & Regex sweep for vague phrasing, marketing language, meta-questions. \\
      & A2 BiasStats             & \textsc{always} & $\chi^2$ on correct-answer position; Mann--Whitney $U$ on correct-vs-distractor length. \\
      & A3 FactEcho              & \textsc{always} & Longest-common-substring ratio between question text and source fact (\textsc{fail} at LCS$\geq$0.65). \\
      & A4 TemplateFingerprint   & \textsc{always} & POS-bigram logistic regression detector for template-induced stylistic regularities (held-out AUC 0.84). \\
    \midrule
    \multirow{5}{*}{B. Tri-judge}
      & B1 TriJudgeAnswer        & \textsc{always} & Claude / GPT / Gemini panel reads question + source fact and votes on the marked-correct option. \\
      & B2 ClosedBookSolvability & \textsc{always} & Same panel, source fact \emph{withheld}: can the question be answered from world knowledge alone? \\
      & B3 UbiquityRisk          & \textsc{always} & Internationally-grown grape stem $\times$ region-class answer $\Rightarrow$ ambiguity flag. \\
      & B4 Ambiguity             & \textsc{esc}    & Tri-judge re-read flags questions with $>$1 defensible answer; invoked when B1 dissent rate elevated. \\
      & B5 VerifierSkip          & \textsc{esc}    & Self-consistency probe across re-prompted panels; invoked on disputed B1 verdicts. \\
    \midrule
    \multirow{4}{*}{C. Determin.}
      & C1 DistractorDifficulty  & \textsc{esc}    & Embedding-distance distractor analysis; invoked when A2 reports length skew. \\
      & C2 CategoryLeak          & \textsc{always} & Wine-type distractor validation; flags red/white/sparkling category mismatches. \\
      & C3 SourceSwap            & \textsc{esc}    & Substitutes alternate source facts to test answer stability; invoked on B1/B2 disagreement. \\
      & C4 DifficultyAudit       & \textsc{always} & Gemini Pro re-rates difficulty; \textsc{fail/warn} when delta $\geq$2 from assigned. \\
    \midrule
    \multirow{3}{*}{D. Corpus stats}
      & D1 SelfPreference        & \textsc{always} & Per-generator-family own-vs-other accuracy on a held-out probe; corpus-level signal. \\
      & D2 DedupCalibration      & \textsc{esc}    & Near-duplicate audit at cosine $\geq$0.92; invoked on suspicious cluster signals. \\
      & D3 SkewAudit             & \textsc{always} & Country / sub-domain over-representation $\chi^2$. \\
    \bottomrule
  \end{tabular}
\end{table}

Of the 14 agents, \textbf{nine are always-run} on every candidate
question; the remaining \textbf{five are escalation-gated} and are
invoked only when an upstream agent flags a corpus-level concern. This
deferred-execution policy keeps routine audit cost bounded
($\sim$\$76 for the full corpus audit reported here, 5h~22m wall)
while preserving full coverage when a defect class is suspected. The
full audit code, prompts, and thresholds are released alongside the
corpus (Appendix~\ref{app:methodology}).

\FloatBarrier
\subsection{Gold-sheet calibration}
\label{sec:gold}
A human gold sheet of 50 stratified questions per release is rated by a
WSET-Diploma reviewer through the released human-review web app
(Appendix~\ref{app:screenshots}). \textbf{15+ gold-sheet rounds} have
been completed across preliminary releases (audit pilots v1--v16) so
that the agent thresholds and $\kappa$ values reported here represent
calibration aggregated over an iterative cycle, not a single batch.
Each round rates against eight rubrics:
\texttt{answer\_correct}, \texttt{distractors\_plausible},
\texttt{not\_ambiguous}, \texttt{source\_faithful},
\texttt{needs\_source}, \texttt{no\_vague\_language},
\texttt{labels\_correct}, and \texttt{verbatim\_copy}. For each
automated agent we compute Cohen's $\kappa$ against the corresponding
human rubric on the gold sheet. \textbf{Agent signals with $\kappa<0.6$
are downweighted to advisory-only and excluded from gating decisions.}

The most consequential calibration result concerns agent
\textbf{B2~ClosedBookSolvability}: against the human reviewer, who
solved only $\approx$12\% of the gold-sheet questions without seeing the
source fact, the LLM tri-judge panel reported $\approx$83\% solvability,
yielding $\kappa\approx0.007$. We interpret this not as a defect of the
benchmark but as a property of the \emph{evaluator}: frontier LLM judges
have absorbed enough wine knowledge during pre-training to over-attribute
``world knowledge'' to questions that humans find non-trivial. We
therefore retain the 1{,}601 B2-flagged questions in the released
corpus, document the finding in the datasheet, and report a
closed-book vs.\ source-grounded contrast in
Section~\ref{sec:eval-cb} that turns the audit's blind spot into a
calibrated diagnostic of memorisation reliance.

\subsection{Release-cycle results}
\label{sec:audit-results}
The 9-agent audit on \texttt{release\_v1.1} (3{,}670 candidate
questions) produced the verdicts summarised in
Table~\ref{tab:audit_results} (Appendix~\ref{app:audit-agents}): A1, A3,
B1, C2 and B3 between them flagged 341 distinct questions for
\textsc{drop}, while C4 re-labelled difficulty on 1{,}259 questions
and B2 flagged 1{,}601 as closed-book-solvable but kept them with
disclosure.

After drops, a follow-up post-evaluation pass (Section~\ref{sec:eval}
and Appendix~\ref{app:eval}) audited the 97 questions that all 16
evaluation configs answered incorrectly: 54 were removed as defects
(wrong ground truth, all-correct options, duplicate options), 9 were
dropped on borderline-review and the remaining 34 retained as
legitimately hard. The final released corpus is 3{,}266 questions.

The C4-driven difficulty re-label was decisive: it shifted the corpus
from 14\% L3+L4 items (the original generator-assigned distribution) to
\textbf{51\% L3+L4} (Table~\ref{tab:difficulty-shift},
Appendix~\ref{app:audit-agents}), bringing the hardest-tier counts above
the entry-tier counts and substantially sharpening
difficulty-stratified analyses (Section~\ref{sec:eval-rank}).

