\section{Applications and Future Work}
\label{sec:future}

OenoBench is a benchmark first, but the construction pipeline behind it
is intended to be reusable. We outline three threads that build on the
released artifacts and methodology, in approximate order of immediate
feasibility.

\subsection{Closing the wine-knowledge gap in low-cost models}
The cost-vs-accuracy frontier (Section~\ref{sec:eval-cost}) shows that
small open-weight models (Llama 3.1 8B, Qwen 2.5 7B, Llama 3.3 70B)
trail proprietary frontier models by 20--30~pp on this benchmark, even
though the gap shrinks to 10--15~pp on broad benchmarks like MMLU. The
38{,}104-fact corpus, with paragraph-length explanations grounded in
source URLs, is a natural \emph{supervised fine-tuning} target for a
wine-specialist small model. Our preliminary plan is a two-stage
recipe: (i) instruction-style fine-tuning on a held-out quartile of
the released questions paired with their supporting facts, so the
model learns to consume a source fact and reason through it; and (ii)
LoRA adaptation on the full 38{,}104-fact corpus, which the released
schema exposes as ready-made fact-question-source triples. Both
stages are accessible to anyone with consumer GPUs and the released
data --- they do not require pre-training compute or proprietary
weights. The contextual / source-grounded slice
(Section~\ref{sec:eval-cb}) provides a clean evaluation surface that
is harder to game by parametric memorisation, so the gain measured
against frontier models is a faithful proxy for genuine wine
reasoning. We expect a Llama-3.3-70B-class model adapted this way to
recover the bulk of the GPT-5-mini gap at $\approx$1\% of proprietary
inference cost, opening realistic deployment paths for
sommelier-tooling and wine-education applications that are
cost-sensitive at high volume.

\subsection{Case-based evaluation with industry partners}
Multiple-choice factual tests have ceilings: even a perfect
OenoBench score does not establish that a model can act usefully in
real workflows. We are scoping an \textbf{applied case-based dataset}
in collaboration with industry partners along three personas:

\begin{itemize}\itemsep -1pt
  \item \emph{Sommelier $\rightarrow$ customer service.} Realistic
    consumer prompts (``what red would pair with a duck confit and
    please my mother who likes Pinot but doesn't want anything tannic''),
    rated by certified sommeliers against the model's
    recommendation, justification, and substitutions.
  \item \emph{Winemaker $\rightarrow$ blending decisions.} Vintage
    write-ups, lab analyses, and regulatory constraints fed in as
    context; model outputs a blending plan; rated by working
    winemakers on technical correctness, regulatory compliance, and
    stylistic intent.
  \item \emph{Viticulturist $\rightarrow$ vineyard decisions.}
    Multi-year weather records, soil and disease-pressure reports,
    canopy and yield data fed in as context; the model recommends
    canopy-management, irrigation, harvest-timing, and pest-control
    interventions; rated by working viticulturists against the
    decisions actually taken in the same vintage.
\end{itemize}

Such a dataset cannot be built from scraped facts alone --- it requires
domain-expert annotation of free-form outputs. The construction
pipeline of OenoBench (multi-strategy generation, multi-agent audit,
gold-sheet calibration) carries over: scenario-style generation
templates can produce candidate prompts; the same nine-agent audit can
flag obvious failure modes; and the human-review web app
(Appendix~\ref{app:screenshots}) is already designed to support
multi-reviewer IRR aggregation. We treat OenoBench as the
\emph{factual-recall floor} of an eventually two-tier evaluation:
factual knowledge must be near-saturated before applied reasoning can
be validly measured.

\subsection{Generalising the LLM-driven scrape-to-audit pipeline}
The most consequential contribution of this work is methodological,
not domain-specific. The pipeline elements --- (i) a tier-of-authority
source taxonomy, (ii) atomic-fact extraction with paraphrase
enforcement, (iii) multi-strategy multi-model question generation with
a per-model quota, (iv) an automated multi-agent audit calibrated
against humans via $\kappa$, and (v) a closed-book pre-screen that
isolates parametric leakage --- are domain-agnostic. We have
implemented them as separable modules with clear interfaces;
replacing the source-tier configuration and the domain taxonomy is
sufficient to retarget the pipeline to a different field.

We see three near-term targets. First, \emph{horticulture and
agronomy} share many of wine's structural features (regulated
appellations, peer-reviewed agronomic journals, certification ladders
for advisors) and would benefit from the same provenance discipline.
Second, \emph{regulated medicine} (clinical guidelines, drug
formularies) has the strongest tier-of-authority structure in any
field and the most acute need for source-traceable benchmarks; medical
benchmarks today rely on board-exam questions which are not
necessarily aligned with practice. Third, \emph{financial regulation
and accounting} has tiered authority (FASB, IFRS, jurisdictional
filings) and a clear professional ladder (CFA, CPA), and would benefit
from a benchmark whose questions are explicitly anchored in citable
regulation. In each case, the pipeline reduces what is currently a
months-long expert-authoring effort to a weeks-long curation effort,
provided the tier-of-authority configuration is done carefully. The
released code and the methodology in Sections~\ref{sec:dataset} and
\ref{sec:audit} are intended as a recipe for that retargeting.
