\section{Limitations}
\label{sec:limitations}

\paragraph{Language and cultural scope.} OenoBench is currently
English-only. The Tier-2 source mix (Wikipedia 34\%, Wikidata 31\%) is
itself English-skewed, and the corpus inherits a geographic bias toward
European (especially French, Italian, Spanish) and New-World canonical
regions. Emerging wine cultures (China, India, much of Eastern Europe)
are under-represented in absolute counts. Multilingual extension is
the largest single gap and is the most natural next-version target.

\paragraph{Source skew within domains.} Producer and wine-business
domains are smaller (515 and 250 questions respectively) than wine
regions (1{,}108) and grape varieties (766) because authoritative
producer-level and business-level open data is scarcer than
appellation-level data. The C4 difficulty re-label
(Section~\ref{sec:audit}) shifted the corpus toward harder items but
cannot create coverage that did not exist; the per-domain accuracy
ceiling on \emph{wine\_business} (\textbf{56.5\% mean across 16 configs},
vs.\ 79\% on producers) reflects both the hardness of the domain and
its sparser fact pool.

\paragraph{Snapshot vs.\ moving target.} Wine regulation,
classifications, and producer ownership change on a multi-year cadence
(INAO appellation revisions, DOCG promotions, estate sales). The
released corpus is a snapshot dated 2026-04-01 and will require
periodic re-extraction; we release the scrapers and provenance
metadata so this is mechanically reproducible.

\paragraph{Closed-book audit calibration.} The B2 ClosedBookSolvability
agent shows $\kappa\approx0.007$ with humans on the gold sheet
(Section~\ref{sec:gold}). Rather than drop the affected questions, we
keep them with explicit disclosure and report the closed-book vs.\
contextual contrast in Section~\ref{sec:eval-cb}. Downstream users who
prefer a strictly source-grounded subset can use the contextual slice;
those who want pure recall can use the closed-book slice. The
documentation is a load-bearing part of the dataset, not a footnote.

\paragraph{Self-preference is not fully neutralised.} The Anthropic
$+9$~pp positive SPS (Section~\ref{sec:eval-sps}) implies the
multi-model generation strategy did not fully neutralise stylistic
fingerprints. We disclose per-config SPS as a first-class diagnostic
rather than removing the affected items, but downstream comparisons
between Anthropic and other-family models on the full corpus should
be treated with the SPS in mind.

