\section{Released Artifacts and Reproducibility}
\label{app:artifacts}

\subsection{Released artifacts}

\begin{itemize}\itemsep -1pt
  \item \textbf{Dataset (HuggingFace).}
    \url{https://huggingface.co/datasets/oenobench-anon/oenobench} —
    \texttt{release\_v1.2}, 3{,}266 questions, Parquet test split,
    \texttt{README.md} datasheet, \texttt{croissant.json} manifest.
    License: CC-BY-SA-4.0. Versioning is permanent: prior releases
    remain accessible via revision tags.
  \item \textbf{Code (GitHub).}
    \url{https://github.com/nikitahudov/oenobench} — full pipeline:
    35 scrapers, 5 question generators, 14 audit agents, the human
    review web app, and the monitoring dashboard. Apache 2.0.
  \item \textbf{Process log.} \texttt{docs/PROCESS\_LOG.md} —
    chronological lab-notebook of every phase shipped, with sources,
    methodology, quality-control counts, and decision rationale, in
    the format prescribed for the methodology sections of this paper.
  \item \textbf{Audit reports.} \texttt{docs/QUALITY\_AUDIT\_REPORT.md},
    \texttt{docs/RELEASE\_V1\_2\_AUDIT\_ACTIONS.md},
    \texttt{docs/GOLD\_CALIBRATION\_ANALYSIS.md},
    \texttt{data/reports/zero\_correct\_97\_audit.md}.
  \item \textbf{Eval reports.}
    \texttt{data/reports/eval\_release\_v1\_2\_full\_cleaned.md} (the
    16-config × 3{,}266-Q run reported in this paper).
\end{itemize}

\subsection{Reproducibility scripts}

The construction pipeline is driven by a small number of shell scripts
in \texttt{scripts/}:

\begin{itemize}\itemsep -1pt
  \item \texttt{run\_all\_scrapers.sh} — orchestrates the 35 scrapers
    end-to-end. Each scraper writes a timestamped log to
    \texttt{data/logs/}.
  \item \texttt{run\_release\_v1\_build.sh} — full generation pipeline
    invocation; idempotent and resume-safe via stamped tags.
  \item \texttt{export\_release\_v1\_2\_to\_parquet.py} — produces the
    HuggingFace Parquet directly from Postgres; the released file
    is the byte-identical output of this script.
  \item \texttt{build\_smart\_review\_sheet.py} — generates a 50-question
    stratified gold-sheet review batch (random + critical-FAIL +
    borderline-WARN strata).
  \item \texttt{tag\_audit\_actions.py} — applies the audit drop /
    relabel policy to a tagged corpus; this is the script that
    produced the \texttt{release\_v1.2} state from
    \texttt{release\_v1.1}.
\end{itemize}

\subsection{Database schema}

The released schema is initialised by the migrations under
\texttt{config/postgres/} (six idempotent files, applied in order on
container startup):
\texttt{init.sql} (sources, facts, questions, question\_facts,
generation\_metadata, evaluation\_runs, evaluation\_answers,
human\_reviews),
\texttt{002\_audit\_schema.sql} (audit\_runs, audit\_findings,
audit\_gold\_labels, audit\_severity enum),
\texttt{003\_sample\_schema.sql} (mirror schema for the Phase~5
sample-DB eval),
\texttt{003\_cb\_reserve.sql} (closed-book reserve pool tagging),
\texttt{004\_eval\_telemetry.sql} (provider, tokens, reasoning\_config,
latency columns on \texttt{evaluation\_answers}),
\texttt{005\_or\_cost\_telemetry.sql} (OpenRouter authoritative cost
columns).

The released schema is documented in code
(\texttt{config/postgres/}); the load-bearing tables are
\texttt{sources} (registry), \texttt{facts} (atomic facts grounded by
source), \texttt{questions} + \texttt{question\_facts} (corpus and
fact-question links), \texttt{generation\_metadata} (per-question
generator and strategy), \texttt{audit\_findings} (per-agent
verdicts), and \texttt{human\_reviews} (gold-sheet ratings).

\subsection{Compute and cost}

The full evaluation reported in Section~\ref{sec:eval} ran in
\textbf{120 minutes 34 seconds} on a single VM driving 16 OpenRouter
configurations in parallel. \textbf{Total LLM API spend across the
entire project was \$783}, paid out-of-pocket to OpenRouter and
covering all generation pilots, audit cycles, gold-sheet calibration
runs, and the final 16-config evaluation. No GPU compute was used;
all model inference was via OpenRouter (a unified API gateway). The
release artefacts include all per-call telemetry (provider, tokens,
reasoning configuration, p50/p95 latency, OR-authoritative cost) for
the full evaluation run; the per-config cost ledger is reproduced
inline as Table~\ref{tab:cost-ledger-app}.

\begin{table}[h]
  \centering
  \footnotesize
  \caption{Per-config cost ledger for the full 16-config evaluation
    (3{,}266 questions per config). Effective OpenRouter spend.}
  \label{tab:cost-ledger-app}
  \begin{tabular}{lrrr}
    \toprule
    Config & Total cost & Correct ans. & Cost / correct \\
    \midrule
    llama-3.1-8b               & \$0.01 & 1{,}976 & \$0.0000 \\
    llama-3.3-70b              & \$0.04 & 2{,}190 & \$0.0000 \\
    gemini-2.5-flash           & \$0.12 & 2{,}454 & \$0.0000 \\
    deepseek-v3                & \$0.12 & 2{,}295 & \$0.0001 \\
    qwen-2.5-7b                & \$0.12 & 1{,}860 & \$0.0001 \\
    qwen-2.5-72b               & \$0.15 & 2{,}202 & \$0.0001 \\
    claude-haiku-4.5           & \$0.44 & 1{,}741 & \$0.0003 \\
    mistral-large-2411         & \$0.87 & 2{,}256 & \$0.0004 \\
    gpt-5-mini                 & \$2.82 & 2{,}561 & \$0.0011 \\
    claude-opus-4.7            & \$3.35 & 2{,}647 & \$0.0013 \\
    claude-opus-4.7-thinking   & \$3.53 & 2{,}645 & \$0.0013 \\
    deepseek-r1                & \$10.54 & 2{,}517 & \$0.0042 \\
    o3                         & \$11.80 & 2{,}729 & \$0.0043 \\
    gemini-2.5-pro-thinking    & \$13.06 & 2{,}698 & \$0.0048 \\
    gpt-5                      & \$21.90 & 2{,}704 & \$0.0081 \\
    gemini-2.5-pro             & \$29.47 & 2{,}669 & \$0.0110 \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Per-source licensing}
\label{sec:licensing}

Section~\ref{sec:sources} states that every fact in the corpus traces
to a public-record source or to a source distributed under a licence
that permits scraping and redistribution. We give the per-source
breakdown in Table~\ref{tab:licensing}, grouping the
35 scrapers' source families by tier and licence basis. Each row
maps to one or more rows in the released \texttt{sources} table, where
per-row \texttt{name}, \texttt{url}, \texttt{tier}, and access timestamp
are recorded for every fact (\texttt{facts.source\_id}~$\rightarrow$
\texttt{sources.id}). Wikipedia and Wikidata together account for 65.3\%
of facts and propagate their share-alike / public-domain dedications
through the \texttt{release\_v1.2} CC-BY-SA-4.0 licence. Government
records (Tier~1, 19.6\% of facts) are either explicit open-data
licences (INAO Licence Ouverte~2.0, EU re-use Decision 2011/833/EU) or
US-Government works in the public domain
(17~U.S.C.~\textsection 105: TTB, USDA Extension, UC IPM).

\begin{table}[h]
  \centering
  \footnotesize
  \caption{Per-source licensing for OenoBench's 35 scrapers, grouped by
    source family. ``Share'' is the percentage of the 38{,}104-fact
    corpus contributed; ``Tier'' is the source-of-authority label from
    Section~\ref{sec:sources}. Counts are computed directly from the
    \texttt{facts}~$\bowtie$~\texttt{sources} join in the released
    schema.}
  \label{tab:licensing}
  \begin{tabular}{p{0.31\linewidth}lp{0.30\linewidth}r}
    \toprule
    Source family & Tier & Licence / legal basis & Share \\
    \midrule
    Wikipedia (MediaWiki API)                                            & T2          & CC-BY-SA 4.0                                           & 34.4\% \\
    Wikidata (SPARQL)                                                    & T1 / T2     & CC0 1.0                                                & 30.3\% \\
    HuggingFace \texttt{spawn99/wine-reviews}                            & T2          & HuggingFace dataset terms (open redistribution)        &  8.5\% \\
    UC Davis (AVA Project, FPS, Wine Ontology)                           & T1          & Open / CC-BY (UC Davis Library)                        &  5.7\% \\
    UC IPM \& USDA Extension (eXtension, PSU/OSU)                        & T1 / T2     & Public domain --- US Gov.\ work (17 USC \S105)         &  4.7\% \\
    Kaggle: wine-reviews (Wine Enthusiast scrape)                        & T3          & Kaggle dataset terms (research use)                    &  3.8\% \\
    INAO (data.gouv.fr open-data)                                        & T1          & Licence Ouverte 2.0 (Etalab)                           &  3.9\% \\
    Wine consortia + national bodies (CIVB, BIVB, CIVC, IT consortia, NZ Wine, Austrian Wine, Deutsches Weininstitut, Spanish DO) & T2 & Industry-body publications, educational use & 3.2\% \\
    OENO One                                                             & T2          & CC-BY 4.0 (open-access journal)                        &  2.0\% \\
    TTB (27 CFR Part 4, Established AVAs, Approved Grape Names)          & T1          & Public domain --- US Gov.\ work                        &  1.3\% \\
    National ministries + EU registries (MASAF, MAPA, IVV, IVDP, EUR-Lex, GIView) & T1 / T2 & Government public records / EU Decision 2011/833/EU & 1.3\% \\
    OIV publications (Code of Oenological Practices, statistics)         & T1          & Open access --- intergov.\ organisation                &  0.2\% \\
    Vitis (Hochschule Geisenheim)                                        & T2          & Open access                                            &  0.3\% \\
    National reference databases (CA, UK, HR/SI, HU/GE, LB/IL, +regions) & T2          & Reference / official-body content                      &  0.3\% \\
    Kaggle: wine-quality (UCI ML Repository)                             & T2          & CC-BY 4.0 (UCI)                                        &  0.2\% \\
    \bottomrule
  \end{tabular}
\end{table}

The released corpus, including this paper's quoted statistics, is
distributed under \textbf{CC-BY-SA 4.0}. The construction code is
released under \textbf{Apache 2.0}. Verbatim source text is never
stored: every fact is paraphrased atomically (Section~\ref{sec:extraction})
and a paraphrase guard at audit time (agent~A3) re-checks for
verbatim leakage. We retain \texttt{accessed\_date} and a per-source
\texttt{content\_date} for every fact, so dataset users can audit
freshness against original sources.

\subsection{Test status}

771 of 771 unit tests pass on \texttt{main} as of the camera-ready
build. Tests cover the fact-processing pipeline, the five generation
strategies, all 14 audit agents, the orchestrator, the closed-book
gate, the eval harness (slot dispatch, cost computation,
reasoning-mode prompt assembly), and the review-app endpoints.
