\section*{NeurIPS Paper Checklist}

\begin{enumerate}

\item {\bf Claims}
    \item[] Question: Do the main claims made in the abstract and introduction accurately reflect the paper's contributions and scope?
    \item[] Answer: \answerYes{}
    \item[] Justification: Section~\ref{sec:intro} lists four contributions, and each is supported by a numbered section: dataset construction (Section~\ref{sec:dataset}), automated audit (Section~\ref{sec:audit}), bias-aware evaluation (Section~\ref{sec:eval}). The abstract's headline numbers (3{,}266 questions, 16-config eval, +32.6~pp closed-book vs.\ contextual gap) are reproduced with full tables in Appendix~\ref{app:eval}.

\item {\bf Limitations}
    \item[] Question: Does the paper discuss the limitations of the work performed by the authors?
    \item[] Answer: \answerYes{}
    \item[] Justification: Section~\ref{sec:limitations} discusses six limitations explicitly, including English-only scope, geographic skew, snapshot vs.\ moving target, B2 audit calibration ceiling, residual self-preference, and single-reviewer gold sheet.

\item {\bf Theory assumptions and proofs}
    \item[] Question: For each theoretical result, does the paper provide the full set of assumptions and a complete (and correct) proof?
    \item[] Answer: \answerNA{}
    \item[] Justification: This is a dataset-and-benchmark paper; no formal theoretical results are claimed.

\item {\bf Experimental result reproducibility}
    \item[] Question: Does the paper fully disclose all the information needed to reproduce the main experimental results of the paper?
    \item[] Answer: \answerYes{}
    \item[] Justification: Appendix~\ref{app:artifacts} lists the construction scripts, the dataset URL, the model slate, the per-call telemetry available alongside the released corpus, and the deterministic build pipeline. Section~\ref{sec:eval} reports run id, wall time, total cost, and exact config strings.

\item {\bf Open access to data and code}
    \item[] Question: Does the paper provide open access to the data and code, with sufficient instructions to faithfully reproduce the main experimental results, as described in supplemental material?
    \item[] Answer: \answerYes{}
    \item[] Justification: Code at \url{https://github.com/nikitahudov/oenobench} (Apache~2.0); data at \url{https://huggingface.co/datasets/oenobench/oenobench} (CC-BY-SA-4.0). Exact reproduction commands are documented in Appendix~\ref{app:artifacts}.

\item {\bf Experimental setting/details}
    \item[] Question: Does the paper specify all the training and test details necessary to understand the results?
    \item[] Answer: \answerYes{}
    \item[] Justification: Section~\ref{sec:eval} specifies the 16-config slate, single-letter output protocol (A--D, \texttt{max\_tokens=5}, five-stop fallback). Appendix~\ref{app:eval} gives full per-config × per-domain × per-strategy × per-difficulty tables. Appendix~\ref{app:methodology} gives audit-agent thresholds and prompt summaries.

\item {\bf Experiment statistical significance}
    \item[] Question: Does the paper report error bars suitably and correctly defined or other appropriate information about the statistical significance of the experiments?
    \item[] Answer: \answerYes{}
    \item[] Justification: Reasoning lift, self-preference scores, and closed-book vs.\ contextual deltas are all reported with 95\% bootstrap confidence intervals (1{,}000 resamples), with the bootstrap procedure documented in Section~\ref{sec:eval}.

\item {\bf Experiments compute resources}
    \item[] Question: For each experiment, does the paper provide sufficient information on the computer resources needed to reproduce the experiments?
    \item[] Answer: \answerYes{}
    \item[] Justification: Appendix~\ref{app:artifacts} reports total wall time (120~min~34~s), total LLM calls (52{,}256), total cost (\$98.33 effective), and the deployment topology (single VM driving 16 OpenRouter configurations in parallel; no GPU compute).

\item {\bf Code of ethics}
    \item[] Question: Does the research conducted in the paper conform, in every respect, with the NeurIPS Code of Ethics?
    \item[] Answer: \answerYes{}
    \item[] Justification: All sources used are public-record; no human subjects research was conducted (the gold-sheet reviewer is the lead author); responsible-use guidance is given in the Datasheet (Appendix~\ref{app:datasheet}, ``Uses'') and in Section~\ref{sec:limitations}.

\item {\bf Broader impacts}
    \item[] Question: Does the paper discuss both potential positive societal impacts and negative societal impacts of the work performed?
    \item[] Answer: \answerYes{}
    \item[] Justification: The Datasheet (Appendix~\ref{app:datasheet}) covers alcohol-context and discouraged uses; source-licensing and the non-fabrication guarantee are documented in Section~\ref{sec:sources}; personal-data scope and the no-private-individuals constraint are in the Datasheet ``Composition''. Section~\ref{sec:future} discusses positive applications including specialist-model fine-tuning and pipeline retargeting to other expert domains.

\item {\bf Safeguards}
    \item[] Question: Does the paper describe safeguards that have been put in place for responsible release of data or models that have a high risk for misuse?
    \item[] Answer: \answerYes{}
    \item[] Justification: The dataset is text-only multiple-choice questions with public-record entity names; no scraped images or personal-data risks. We document discouraged uses in the Datasheet (Appendix~\ref{app:datasheet}, ``Uses'') including the recommendation against retargeting the pipeline to high-stakes domains without expert review.

\item {\bf Licenses for existing assets}
    \item[] Question: Are the creators or original owners of assets used in the paper properly credited and are the license and terms of use explicitly mentioned and properly respected?
    \item[] Answer: \answerYes{}
    \item[] Justification: Source-tier table in Section~\ref{sec:sources} credits all major sources with licenses (Wikipedia CC-BY-SA, Wikidata CC0, INAO Licence Ouverte, TTB public domain, etc.). Per-fact source URLs are released alongside the corpus.

\item {\bf New assets}
    \item[] Question: Are new assets introduced in the paper well documented and is the documentation provided alongside the assets?
    \item[] Answer: \answerYes{}
    \item[] Justification: A full Datasheet is in Appendix~\ref{app:datasheet}; a Croissant manifest \citep{koehn2024croissant} ships with the HuggingFace release; all 9 audit agents, 5 generators, and 35 scrapers are documented in source.

\item {\bf Crowdsourcing and research with human subjects}
    \item[] Question: For crowdsourcing experiments and research with human subjects, does the paper include the full text of instructions given to participants and screenshots, if applicable, as well as details about compensation?
    \item[] Answer: \answerNA{}
    \item[] Justification: No crowdsourcing or third-party human-subjects research. Gold-sheet ratings were produced by the lead author (a WSET-Diploma holder); the review web app screenshots in Appendix~\ref{app:screenshots} document the rubric and instructions.

\item {\bf Institutional review board (IRB) approvals or equivalent for research with human subjects}
    \item[] Question: Does the paper describe potential risks incurred by study participants, whether such risks were disclosed to the subjects, and whether IRB approvals were obtained?
    \item[] Answer: \answerNA{}
    \item[] Justification: As noted in Appendix~\ref{app:datasheet}, the work involves no human subjects research distinct from data-quality assurance by the lead author.

\item {\bf Declaration of LLM usage}
    \item[] Question: Does the paper describe the usage of LLMs if it is an important, original, or non-standard component of the core methods in this research?
    \item[] Answer: \answerYes{}
    \item[] Justification: LLMs are central to the methodology (multi-strategy question generation across five model families, nine-agent automated audit including a tri-judge panel, closed-book solvability pre-screen). Section~\ref{sec:dataset} and Section~\ref{sec:audit} describe their usage; Section~\ref{sec:sources} and Appendix~\ref{app:methodology} document the explicit fact-grounding constraint that prevents LLMs from being used as the source of factual claims.

\end{enumerate}
